Paper_stuff

### 2023-12-29 Paper_stuff.Rmd
Updated demographic table.

## Rename and Recode variables 
We can change the current variables to make them easier to interpret. 
```{r}
#recode varaibles
Mothership <- mutate(Mothership, 
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                          "1"="<Grade 12",
                          "2"="HS Diploma or GED",
                          "3"="HS Diploma or GED",
                          "4"="Some College/Associates Degree",
                          "5"="Some College/Associates Degree",
                          "6"="Bachelors Degree",
                          "7"="Bachelors Degree",
                          "8"="Grad Degree"),
                     Gender_1 = as.factor(Gender_1),
                     Gender_1 = recode(Gender_1,
                          "0"="Female",
                          "1"="Male",
                          "2"="Non-Binary",
                          "3"="Other",
                          "4"="Other"),
                     Relationship_1 = as.factor(Relationship_1),
                     Relationship_1 = recode(Relationship_1,
                          "0"="Married or Cohabitating",
                          "1"="Married or Cohabitating",
                          "2"="Widowed or Seperated",
                          "3"="Widowed or Separated",
                          "4"="Divorced",
                          "5"="Single or Never Married"),
                     Sexuality_1 = as.factor(Sexuality_1),
                     Sexuality_1 = recode(Sexuality_1,
                          "1"="Straight",
                          "2"="Gay",
                          "3"="Bisexual",
                          "4"="Other"),
                     IPT_track_1 = as.factor(IPT_track_1),
                     IPT_track_1 = recode(IPT_track_1,
                          "0"="General",
                          "1"="Trauma",
                          "2"="Young Adult",
                          "3"="BPD"),
                     Race_1 = as.factor(Race_1),
                     Race_1 = recode(Race_1,
                                     "0"="White",
                                     "1"="Black",
                                     "2"="Hispanic",
                                     "3"="Asian",
                                     "4"="Portugese",
                                     "5"="Other"),
                    DC_status_1 = as.factor(DC_status_1),
                    DC_status_1 = recode(DC_status_1,
                                      "1" ="Inpatient",
                                      "2" ="PHP",
                                      "3" ="APS",
                                      "4" ="Psychatrist",
                                      "5" ="PCP",
                                      "6" ="Another Physican",
                                      "7" ="Therapist",
                                      "8"="Withdrew (AMA)",
                                      "9"="Other",
                                      "10"="Other",
                                      "11"="Other",
                                      "17"="Other",
                                      "0" ="Other"),

@@

str(Mothership$Education_1)
```

@@

              #deprssion values Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)"
        BL_Dep_level = as.factor(ifelse(BL_CUDOS > 10 & BL_CUDOS <= 20, "Minimal",
                                 ifelse(BL_CUDOS > 20 & BL_CUDOS <= 30, "Mild",
                                 ifelse(BL_CUDOS > 10 & BL_CUDOS <= 45, "Moderate",
                                 ifelse(BL_CUDOS > 45, "Severe",
                                 ifelse(is.na(BL_CUDOS), NA, "Remission"
                                )))))),
        BL_Anx_level = as.factor(ifelse(BL_CUXOS > 10 & BL_CUXOS <= 20, "Minimal",
                                 ifelse(BL_CUXOS > 20 & BL_CUXOS <= 30, "Mild",
                                 ifelse(BL_CUXOS > 10 & BL_CUXOS <= 45, "Moderate",
                                 ifelse(BL_CUXOS > 45, "Severe",
                                 ifelse(is.na(BL_CUXOS), NA, "Remission"
                                )))))),
        Post_Dep_level = as.factor(ifelse(CUDOS_post > 10 & CUDOS_post <= 20, "Minimal",
                                 ifelse(CUDOS_post > 20 & CUDOS_post <= 30, "Mild",
                                 ifelse(CUDOS_post > 10 & CUDOS_post <= 45, "Moderate",
                                 ifelse(CUDOS_post > 45, "Severe",
                                 ifelse(is.na(CUDOS_post), NA, "Remission"
                                )))))),
        Post_Anx_level = as.factor(ifelse(CUXOS_post > 10 & CUXOS_post <= 20, "Minimal",
                                 ifelse(CUXOS_post > 20 & CUXOS_post <= 30, "Mild",
                                 ifelse(CUXOS_post > 10 & CUXOS_post <= 45, "Moderate",
                                 ifelse(CUXOS_post > 45, "Severe",
                                 ifelse(is.na(CUXOS_post), NA, "Remission"
                                )))))))
    ```
    ```{r}
#devtools::install_github("AWKruijt/JT-RCI")

@@

@@

    ```{r}
#7. create new DF with Varaibles we want

@@

#Demographic tab
Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1, data=Demo_tab_df))
colnames(Demo_tab) <- c("Demographic","Total Sample")
Demo_tab

>>>>

## Rename and Recode variables 
We can change the current variables to make them easier to interpret. 
```{r}
#recode varaibles
Mothership <- mutate(Mothership, 
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                          "0"="<Grade 12",
                          "1"="<Grade 12",
                          "2"="HS Diploma or GED",
                          "3"="HS Diploma or GED",
                          "4"="Some College/Associates Degree",
                          "5"="Some College/Associates Degree",
                          "6"="Bachelors Degree",
                          "7"="Bachelors Degree",
                          "8"="Grad Degree"),
                     Gender_1 = as.factor(Gender_1),
                     Gender_1 = recode(Gender_1,
                          "0"="Female",
                          "1"="Male",
                          "2"="Non-Binary",
                          "3"="Other",
                          "4"="Other"),
                     Relationship_1 = ifelse(Relationship_1 == 8, NA, Relationship_1),
                     Relationship_1 = as.factor(Relationship_1),
                     Relationship_1 = recode(Relationship_1,
                          "0"="Married or Cohabitating",
                          "1"="Married or Cohabitating",
                          "2"="Widowed or Separated",
                          "3"="Widowed or Separated",
                          "4"="Divorced",
                          "5"="Single or Never Married"),
                     Sexuality_1 = as.factor(Sexuality_1),
                     Sexuality_1 = recode(Sexuality_1,
                          "1"="Straight",
                          "2"="Gay",
                          "3"="Bisexual",
                          "4"="Other"),
                     IPT_track_1 = as.factor(IPT_track_1),
                     IPT_track_1 = recode(IPT_track_1,
                          "0"="General",
                          "1"="Trauma",
                          "2"="Young Adult",
                          "3"="BPD"),
                     Race_1 = ifelse(Race_1 == 6, NA, Race_1),
                     Race_1 = as.factor(Race_1),
                     Race_1 = recode(Race_1,
                                     "0"="White",
                                     "1"="Black",
                                     "2"="Hispanic",
                                     "3"="Asian",
                                     "4"="Portugese",
                                     "5"="Other"),
                    DC_status_1 = as.factor(DC_status_1),
                    DC_status_1 = recode(DC_status_1,
                                      "1" ="Inpatient",
                                      "2" ="PHP",
                                      "3" ="APS",
                                      "4" ="Psychatrist",
                                      "5" ="PCP",
                                      "6" ="Another Physican",
                                      "7" ="Therapist",
                                      "8"="Withdrew (AMA)",
                                      "9"="Other",
                                      "10"="Other",
                                      "11"="Other",
                                      "17"="Other",
                                      "0" ="Other"),

@@

@@

              #deprssion values Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)"
        BL_Dep_level = as.factor(ifelse(BL_CUDOS > 10 & BL_CUDOS <= 20, "Minimal",
                                 ifelse(BL_CUDOS > 20 & BL_CUDOS <= 30, "Mild",
                                 ifelse(BL_CUDOS > 10 & BL_CUDOS <= 45, "Moderate",
                                 ifelse(BL_CUDOS > 45, "Severe",
                                 ifelse(is.na(BL_CUDOS), NA, "Remission"
                                )))))),
        BL_Anx_level = as.factor(ifelse(BL_CUXOS > 10 & BL_CUXOS <= 20, "Minimal",
                                 ifelse(BL_CUXOS > 20 & BL_CUXOS <= 30, "Mild",
                                 ifelse(BL_CUXOS > 10 & BL_CUXOS <= 45, "Moderate",
                                 ifelse(BL_CUXOS > 45, "Severe",
                                 ifelse(is.na(BL_CUXOS), NA, "Remission"
                                )))))),
        Post_Dep_level = as.factor(ifelse(CUDOS_post > 10 & CUDOS_post <= 20, "Minimal",
                                 ifelse(CUDOS_post > 20 & CUDOS_post <= 30, "Mild",
                                 ifelse(CUDOS_post > 10 & CUDOS_post <= 45, "Moderate",
                                 ifelse(CUDOS_post > 45, "Severe",
                                 ifelse(is.na(CUDOS_post), NA, "Remission"
                                )))))),
        Post_Anx_level = as.factor(ifelse(CUXOS_post > 10 & CUXOS_post <= 20, "Minimal",
                                 ifelse(CUXOS_post > 20 & CUXOS_post <= 30, "Mild",
                                 ifelse(CUXOS_post > 10 & CUXOS_post <= 45, "Moderate",
                                 ifelse(CUXOS_post > 45, "Severe",
                                 ifelse(is.na(CUXOS_post), NA, "Remission"
                                )))))))
    ```

Responders
```{r}
#devtools::install_github("AWKruijt/JT-RCI")

@@

RCI
    ```{r}
Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
      )),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
      )),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

@@

AnxDep_PrePost
    ```{r}
#7. create new DF with Varaibles we want

@@

#Demographic tab
Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1, data=Demo_tab_df))
colnames(Demo_tab) <- c("Demographic","Total Sample")
view(Demo_tab)
